---
title: "Simulation1_result"
author: "Rui Hu"
date: "11/6/2021"
output: pdf_document
---

```{R include=FALSE}
library(ggplot2)
library(gridExtra)
library(plyr)
library(knitr)
library(dplyr)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

## 0 Simulation setting   

$$W_1 \sim Unif(-1,1)$$
$$W_2 \sim Unif(-1,1)$$
$$W_3 \sim Bernoulli(0.5)$$
$$A \sim Bernoulli(\pi_0) \ where \ \pi_0=0.5+\frac{1}{3}W_1$$
$$Y \sim N(\mu_0,1) \ where \ \mu_0=0.1+\beta_1A+\beta_2(W_1^2+W_3)+W_1+W_2^2$$
     
$$\tau(W)=\beta_1+\beta_2(W_1^2+W_3)$$

$$\beta=(\beta_1,\beta_2)\in \{(0,0.25),\ (0.25,0.25), \ (0.25,0),\ (0,0)\}$$
$$n\in\{100,\ 250, \ 500,\ 750,\ 1000\}$$
```{r echo=FALSE}
# 1 beta <- c(0, 0.25)
# 2 beta <- c(0.25, 0.25)
# 3 beta <- c(0.25, 0)
# 4 beta <- c(0, 0)
beta_list <- list(c(0, 0.25), c(0.25, 0.25), c(0.25, 0), c(0, 0))

n <- 500
pi0.array <- c()
mu0.array <- c()
psi0 <- c()
theta0 <- c()

sim.setting.df <- data.frame()
for (beta in beta_list){
  for (i in 1:500){
    pi0 <- function(w) 0.5+(w[,1]/3)
    mu0 <- function(a, w, beta) 0.1 + beta[1]*a + beta[2]*a*(w[,1]^2+w[,3]) + w[,1] + w[,2]^2
  
    W <- data.frame(W1=runif(n, -1, 1), W2=runif(n, -1, 1), W3=rbinom(n, size=1, prob=0.5))
    A <- rbinom(n, size=1, prob=pi0(W))
    Y <- rnorm(n, mean=mu0(A, W, beta), sd=1)
  
    pi0.array[i] <- mean(pi0(W))
    mu0.array[i] <- mean(mu0(A, W, beta))
    psi0[i]<- mean((mu0(1, W, beta) - mu0(0, W, beta))^2)
    theta0[i] <- var((mu0(1, W, beta) - mu0(0, W, beta)))
  }
  # p1 <- ggplot(data.frame(pi0=pi0.array)) + 
  #   geom_density(aes(pi0)) +
  #   ggtitle(label=paste("pi0", paste(beta, collapse = "_")))
  # 
  # p2 <- ggplot(data.frame(mu0=mu0.array)) + 
  #   geom_density(aes(mu0)) +
  #   ggtitle(label=paste("mu0", paste(beta, collapse = "_")))
  # 
  # p3 <- ggplot(data.frame(psi0=psi0)) + 
  #   geom_density(aes(psi0)) +
  #   ggtitle(label=paste("psi0", paste(beta, collapse = "_")))
  # 
  # p4 <- ggplot(data.frame(theta0=theta0)) + 
  #   geom_density(aes(theta0)) +
  #   ggtitle(label=paste("theta0", paste(beta, collapse = "_")))
  # 
  # grid.arrange(p1, p2, p3, p4, ncol=2)
  sim.setting.df <- rbind(sim.setting.df, 
                          data.frame(beta=paste("(",paste(beta, collapse=", "),")", sep=""),
                                     pi0=mean(pi0.array), mu0=mean(mu0.array),
                                     psi0=mean(psi0), theta0=mean(theta0)))
  
}
kable(sim.setting.df, digits = 3, caption="Simulated data distribution under different beta settings")
```



## 1 Estimators    
   
### 1.1 $\beta=(0, 0.25)$   

**Estimator of $\psi_0$**
     
     
```{r echo=FALSE}
load("../Estimator/ests.sim.1.0.25.w.sl.RData")
ret <- subset(ests.sim.1.0.25.w.sl,
              (type %in% c('psi.est', 'theta.est')))[,c("type", "est", "ll", "ul", "n", "j" , "seed")]
optional.ret <- subset(ests.sim.1.0.25.w.sl,
                       (type %in% c('psi.est', 'theta.est', 'psi.plug.in.est', 'psi.one.step.est',
                       'theta.plug.in.est', 'theta.one.step.est')))[,c("type", "est", "n", "j" , "seed")]
pars.ret <- subset(ests.sim.1.0.25.w.sl,
                       (type %in% 'pars'))[,c("n", "j" , "seed", "psi0", "theta0")]
ests.sim.1.0.25.w.sl.ret <- join(ret, pars.ret, by=c("n", "j", "seed"))
ests.sim.1.0.25.w.sl.optional.ret <- join(optional.ret, pars.ret, by=c("n", "j", "seed"))
psi.summaries <- ddply(subset(ests.sim.1.0.25.w.sl.optional.ret, 
                                (type %in% c('psi.est', 'psi.plug.in.est', 'psi.one.step.est'))),
                                .(n, type), summarize, na = sum(is.na(est)),
                         cnt = length(est),
                         bias = mean(est - psi0, na.rm=TRUE),
                         var = var(est, na.rm=TRUE),
                         mse = mean((est - psi0)^2, na.rm=TRUE))
```


```{r echo=FALSE}
p2 <- ggplot(subset(ests.sim.1.0.25.w.sl.optional.ret, (type %in% 'psi.est'))) + 
  geom_boxplot(aes(as.factor(n), log(1 + sqrt(n) * (est - psi0)), color=type)) +
  # ggtitle(label=paste("convergence of psi", paste(beta, collapse = "_"))) +
  xlab("n") +
  theme(legend.key.size = unit(0.1,"line"))

p3 <- ggplot(subset(ests.sim.1.0.25.w.sl.optional.ret, (type %in% 'psi.plug.in.est'))) + 
  geom_boxplot(aes(as.factor(n), log(1 + sqrt(n) * (est - psi0)), color=type)) +
  # ggtitle(label=paste("convergence of psi", paste(beta, collapse = "_"))) +
  xlab("n") +
  theme(legend.key.size = unit(0.1,"line"))

p4 <- ggplot(subset(ests.sim.1.0.25.w.sl.optional.ret, (type %in% 'psi.one.step.est'))) + 
  geom_boxplot(aes(as.factor(n), log(1 + sqrt(n) * (est - psi0)), color=type)) +
  # ggtitle(label=paste("convergence of psi", paste(beta, collapse = "_"))) +
  xlab("n") +
  theme(legend.key.size = unit(0.1,"line"))

library(gridExtra)
grid.arrange(p2, p3, p4, ncol=2, top = "beta=(0,0.25)")
```

```{r echo=FALSE}
p2 <- ggplot(psi.summaries) +
  geom_line(aes(n, sqrt(n) * bias, color=type)) +
  theme(legend.key.size = unit(0.1,"line"))

p3 <- ggplot(psi.summaries) +
  geom_line(aes(n, n * mse, color=type)) +
  theme(legend.key.size = unit(0.1,"line"))

p4 <- ggplot(psi.summaries) +
  geom_line(aes(n, n * var, color=type)) +
  theme(legend.key.size = unit(0.1,"line"))
# +
#   coord_cartesian(ylim=c(0,1))

library(gridExtra)
grid.arrange(p2, p3, p4, ncol=2, top = "beta=(0,0.25)")
```

**Estimator of $\theta_0$**

     
```{r echo=FALSE}
theta.summaries <- ddply(subset(ests.sim.1.0.25.w.sl.optional.ret, 
                                (type %in% c('theta.est', 'theta.plug.in.est', 'theta.one.step.est'))),
                                .(n, type), summarize, na = sum(is.na(est)),
                         cnt = length(est),
                         bias = mean(est - theta0, na.rm=TRUE),
                         var = var(est, na.rm=TRUE),
                         mse = mean((est - theta0)^2, na.rm=TRUE))
```

```{r echo=FALSE}
p2 <- ggplot(subset(ests.sim.1.0.25.w.sl.optional.ret, (type %in% 'theta.est'))) + 
  geom_boxplot(aes(as.factor(n), log(1 + sqrt(n) * (est - theta0)), color=type)) +
  # ggtitle(label=paste("convergence of theta", paste(beta, collapse = "_"))) +
  xlab("n") +
  theme(legend.key.size = unit(0.1,"line"))

p3 <- ggplot(subset(ests.sim.1.0.25.w.sl.optional.ret, (type %in% 'theta.plug.in.est'))) + 
  geom_boxplot(aes(as.factor(n), log(1 + sqrt(n) * (est - theta0)), color=type)) +
  # ggtitle(label=paste("convergence of theta", paste(beta, collapse = "_"))) +
  xlab("n") +
  theme(legend.key.size = unit(0.1,"line"))

p4 <- ggplot(subset(ests.sim.1.0.25.w.sl.optional.ret, (type %in% 'theta.one.step.est'))) + 
  geom_boxplot(aes(as.factor(n), log(1 + sqrt(n) * (est - theta0)), color=type)) +
  # ggtitle(label=paste("convergence of theta", paste(beta, collapse = "_"))) +
  xlab("n") +
  theme(legend.key.size = unit(0.1,"line"))

library(gridExtra)
grid.arrange(p2, p3, p4, ncol=2, top = "beta=(0,0.25)")
```

```{r echo=FALSE}
p2 <- ggplot(theta.summaries) +
  geom_line(aes(n, sqrt(n) * bias, color=type)) +
  theme(legend.key.size = unit(0.1,"line"))

p3 <- ggplot(theta.summaries) +
  geom_line(aes(n, n * mse, color=type)) +
  theme(legend.key.size = unit(0.1,"line"))

p4 <- ggplot(theta.summaries) +
  geom_line(aes(n, n * var, color=type)) +
  coord_cartesian(ylim=c(0,1)) +
  theme(legend.key.size = unit(0.1,"line"))

library(gridExtra)
grid.arrange(p2, p3, p4, ncol=2, top = "beta=(0,0.25)")
```


### 1.2 $\beta=(0.25, 0.25)$   

**Estimator of $\psi_0$**
  
     
```{r echo=FALSE}
load("../Estimator/ests.sim.1.25.25.w.sl.RData")
ret <- subset(ests.sim.1.25.25.w.sl,
              (type %in% c('psi.est', 'theta.est')))[,c("type", "est", "ll", "ul", "n", "j" , "seed")]
optional.ret <- subset(ests.sim.1.25.25.w.sl,
                       (type %in% c('psi.est', 'theta.est', 'psi.plug.in.est', 'psi.one.step.est',
                       'theta.plug.in.est', 'theta.one.step.est')))[,c("type", "est", "n", "j" , "seed")]
pars.ret <- subset(ests.sim.1.25.25.w.sl,
                       (type %in% 'pars'))[,c("n", "j" , "seed", "psi0", "theta0")]
ests.sim.1.25.25.w.sl.ret <- join(ret, pars.ret, by=c("n", "j", "seed"))
ests.sim.1.25.25.w.sl.optional.ret <- join(optional.ret, pars.ret, by=c("n", "j", "seed"))
psi.summaries <- ddply(subset(ests.sim.1.25.25.w.sl.optional.ret, 
                                (type %in% c('psi.est', 'psi.plug.in.est', 'psi.one.step.est'))),
                                .(n, type), summarize, na = sum(is.na(est)),
                         cnt = length(est),
                         bias = mean(est - psi0, na.rm=TRUE),
                         var = var(est, na.rm=TRUE),
                         mse = mean((est - psi0)^2, na.rm=TRUE))
```


```{r echo=FALSE}
p2 <- ggplot(subset(ests.sim.1.25.25.w.sl.optional.ret, (type %in% 'psi.est'))) + 
  geom_boxplot(aes(as.factor(n), log(1 + sqrt(n) * (est - psi0)), color=type)) +
  # ggtitle(label=paste("convergence of psi", paste(beta, collapse = "_"))) +
  xlab("n") +
  theme(legend.key.size = unit(0.1,"line"))

p3 <- ggplot(subset(ests.sim.1.25.25.w.sl.optional.ret, (type %in% 'psi.plug.in.est'))) + 
  geom_boxplot(aes(as.factor(n), log(1 + sqrt(n) * (est - psi0)), color=type)) +
  # ggtitle(label=paste("convergence of psi", paste(beta, collapse = "_"))) +
  xlab("n") +
  theme(legend.key.size = unit(0.1,"line"))

p4 <- ggplot(subset(ests.sim.1.25.25.w.sl.optional.ret, (type %in% 'psi.one.step.est'))) + 
  geom_boxplot(aes(as.factor(n), log(1 + sqrt(n) * (est - psi0)), color=type)) +
  # ggtitle(label=paste("convergence of psi", paste(beta, collapse = "_"))) +
  xlab("n") +
  theme(legend.key.size = unit(0.1,"line"))

library(gridExtra)
grid.arrange(p2, p3, p4, ncol=2, top = "beta=(0.25,0.25)")
```

```{r echo=FALSE}
p2 <- ggplot(psi.summaries) +
  geom_line(aes(n, sqrt(n) * bias, color=type)) +
  theme(legend.key.size = unit(0.1,"line"))

p3 <- ggplot(psi.summaries) +
  geom_line(aes(n, n * mse, color=type)) +
  theme(legend.key.size = unit(0.1,"line"))

p4 <- ggplot(psi.summaries) +
  geom_line(aes(n, n * var, color=type)) +
  # coord_cartesian(ylim=c(0,1)) +
  theme(legend.key.size = unit(0.1,"line"))

library(gridExtra)
grid.arrange(p2, p3, p4, ncol=2, top = "beta=(0.25,0.25)")
```

**Estimator of $\theta_0$**
     
```{r echo=FALSE}
theta.summaries <- ddply(subset(ests.sim.1.25.25.w.sl.optional.ret, 
                                (type %in% c('theta.est', 'theta.plug.in.est', 'theta.one.step.est'))),
                                .(n, type), summarize, na = sum(is.na(est)),
                         cnt = length(est),
                         bias = mean(est - theta0, na.rm=TRUE),
                         var = var(est, na.rm=TRUE),
                         mse = mean((est - theta0)^2, na.rm=TRUE))
```

```{r echo=FALSE}
p2 <- ggplot(subset(ests.sim.1.25.25.w.sl.optional.ret, (type %in% 'theta.est'))) + 
  geom_boxplot(aes(as.factor(n), log(1 + sqrt(n) * (est - theta0)), color=type)) +
  # ggtitle(label=paste("convergence of theta", paste(beta, collapse = "_"))) +
  xlab("n") +
  theme(legend.key.size = unit(0.1,"line"))

p3 <- ggplot(subset(ests.sim.1.25.25.w.sl.optional.ret, (type %in% 'theta.plug.in.est'))) + 
  geom_boxplot(aes(as.factor(n), log(1 + sqrt(n) * (est - theta0)), color=type)) +
  # ggtitle(label=paste("convergence of theta", paste(beta, collapse = "_"))) +
  xlab("n") +
  theme(legend.key.size = unit(0.1,"line"))

p4 <- ggplot(subset(ests.sim.1.25.25.w.sl.optional.ret, (type %in% 'theta.one.step.est'))) + 
  geom_boxplot(aes(as.factor(n), log(1 + sqrt(n) * (est - theta0)), color=type)) +
  # ggtitle(label=paste("convergence of theta", paste(beta, collapse = "_"))) +
  xlab("n") +
  theme(legend.key.size = unit(0.1,"line"))

library(gridExtra)
grid.arrange(p2, p3, p4, ncol=2, top = "beta=(0.25,0.25)")
```

```{r echo=FALSE}
p2 <- ggplot(theta.summaries) +
  geom_line(aes(n, sqrt(n) * bias, color=type)) +
  theme(legend.key.size = unit(0.1,"line"))

p3 <- ggplot(theta.summaries) +
  geom_line(aes(n, n * mse, color=type)) +
  theme(legend.key.size = unit(0.1,"line"))

p4 <- ggplot(theta.summaries) +
  geom_line(aes(n, n * var, color=type)) +
  # coord_cartesian(ylim=c(0,1)) +
  theme(legend.key.size = unit(0.1,"line"))

library(gridExtra)
grid.arrange(p2, p3, p4, ncol=2, top = "beta=(0.25,0.25)")
```
    
### 1.3 $\beta=(0.25, 0)$   

**Estimator of $\psi_0$**
  
     
```{r echo=FALSE}
load("../Estimator/ests.sim.1.25.0.w.sl.RData")
ret <- subset(ests.sim.1.25.0.w.sl,
              (type %in% c('psi.est', 'theta.est')))[,c("type", "est", "ll", "ul", "n", "j" , "seed")]
optional.ret <- subset(ests.sim.1.25.0.w.sl,
                       (type %in% c('psi.est', 'theta.est', 'psi.plug.in.est', 'psi.one.step.est',
                       'theta.plug.in.est', 'theta.one.step.est')))[,c("type", "est", "n", "j" , "seed")]
pars.ret <- subset(ests.sim.1.25.0.w.sl,
                       (type %in% 'pars'))[,c("n", "j" , "seed", "psi0", "theta0")]
ests.sim.1.25.0.w.sl.ret <- join(ret, pars.ret, by=c("n", "j", "seed"))
ests.sim.1.25.0.w.sl.optional.ret <- join(optional.ret, pars.ret, by=c("n", "j", "seed"))
psi.summaries <- ddply(subset(ests.sim.1.25.0.w.sl.optional.ret, 
                                (type %in% c('psi.est', 'psi.plug.in.est', 'psi.one.step.est'))),
                                .(n, type), summarize, na = sum(is.na(est)),
                         cnt = length(est),
                         bias = mean(est - psi0, na.rm=TRUE),
                         var = var(est, na.rm=TRUE),
                         mse = mean((est - psi0)^2, na.rm=TRUE))
```


```{r echo=FALSE}
p2 <- ggplot(subset(ests.sim.1.25.0.w.sl.optional.ret, (type %in% 'psi.est'))) + 
  geom_boxplot(aes(as.factor(n), log(1 + sqrt(n) * (est - psi0)), color=type)) +
  # ggtitle(label=paste("convergence of psi", paste(beta, collapse = "_"))) +
  xlab("n") +
  theme(legend.key.size = unit(0.1,"line"))

p3 <- ggplot(subset(ests.sim.1.25.0.w.sl.optional.ret, (type %in% 'psi.plug.in.est'))) + 
  geom_boxplot(aes(as.factor(n), log(1 + sqrt(n) * (est - psi0)), color=type)) +
  # ggtitle(label=paste("convergence of psi", paste(beta, collapse = "_"))) +
  xlab("n") +
  theme(legend.key.size = unit(0.1,"line"))

p4 <- ggplot(subset(ests.sim.1.25.0.w.sl.optional.ret, (type %in% 'psi.one.step.est'))) + 
  geom_boxplot(aes(as.factor(n), log(1 + sqrt(n) * (est - psi0)), color=type)) +
  # ggtitle(label=paste("convergence of psi", paste(beta, collapse = "_"))) +
  xlab("n") +
  theme(legend.key.size = unit(0.1,"line"))

library(gridExtra)
grid.arrange(p2, p3, p4, ncol=2, top = "beta=(0.25,0)")
```

```{r echo=FALSE}
p2 <- ggplot(psi.summaries) +
  geom_line(aes(n, sqrt(n) * bias, color=type)) +
  theme(legend.key.size = unit(0.1,"line"))

p3 <- ggplot(psi.summaries) +
  geom_line(aes(n, n * mse, color=type)) +
  theme(legend.key.size = unit(0.1,"line"))

p4 <- ggplot(psi.summaries) +
  geom_line(aes(n, n * var, color=type)) +
  # coord_cartesian(ylim=c(0,1)) +
  theme(legend.key.size = unit(0.1,"line"))

library(gridExtra)
grid.arrange(p2, p3, p4, ncol=2, top = "beta=(0.25,0)")
```

**Estimator of $\theta_0$**
     
```{r echo=FALSE}
theta.summaries <- ddply(subset(ests.sim.1.25.0.w.sl.optional.ret, 
                                (type %in% c('theta.est', 'theta.plug.in.est', 'theta.one.step.est'))),
                                .(n, type), summarize, na = sum(is.na(est)),
                         cnt = length(est),
                         bias = mean(est - theta0, na.rm=TRUE),
                         var = var(est, na.rm=TRUE),
                         mse = mean((est - theta0)^2, na.rm=TRUE))
```

```{r echo=FALSE}
p2 <- ggplot(subset(ests.sim.1.25.0.w.sl.optional.ret, (type %in% 'theta.est'))) + 
  geom_boxplot(aes(as.factor(n), log(1 + sqrt(n) * (est - theta0)), color=type)) +
  # ggtitle(label=paste("convergence of theta", paste(beta, collapse = "_"))) +
  xlab("n") +
  theme(legend.key.size = unit(0.1,"line"))

p3 <- ggplot(subset(ests.sim.1.25.0.w.sl.optional.ret, (type %in% 'theta.plug.in.est'))) + 
  geom_boxplot(aes(as.factor(n), log(1 + sqrt(n) * (est - theta0)), color=type)) +
  # ggtitle(label=paste("convergence of theta", paste(beta, collapse = "_"))) +
  xlab("n") +
  theme(legend.key.size = unit(0.1,"line"))

p4 <- ggplot(subset(ests.sim.1.25.0.w.sl.optional.ret, (type %in% 'theta.one.step.est'))) + 
  geom_boxplot(aes(as.factor(n), log(1 + sqrt(n) * (est - theta0)), color=type)) +
  # ggtitle(label=paste("convergence of theta", paste(beta, collapse = "_"))) +
  xlab("n") +
  theme(legend.key.size = unit(0.1,"line"))

library(gridExtra)
grid.arrange(p2, p3, p4, ncol=2, top = "beta=(0.25,0)")
```

```{r echo=FALSE}
p2 <- ggplot(theta.summaries) +
  geom_line(aes(n, sqrt(n) * bias, color=type)) +
  theme(legend.key.size = unit(0.1,"line"))

p3 <- ggplot(theta.summaries) +
  geom_line(aes(n, n * mse, color=type)) +
  theme(legend.key.size = unit(0.1,"line"))

p4 <- ggplot(theta.summaries) +
  geom_line(aes(n, n * var, color=type)) +
  # coord_cartesian(ylim=c(0,1)) +
  theme(legend.key.size = unit(0.1,"line"))

library(gridExtra)
grid.arrange(p2, p3, p4, ncol=2, top = "beta=(0.25,0)")
```


### 1.4 $\beta=(0, 0)$   

**Estimator of $\psi_0$**
  
     
```{r echo=FALSE}
load("../Estimator/ests.sim.1.0.0.w.sl.RData")
ret <- subset(ests.sim.1.0.0.w.sl,
              (type %in% c('psi.est', 'theta.est')))[,c("type", "est", "ll", "ul", "n", "j" , "seed")]
optional.ret <- subset(ests.sim.1.0.0.w.sl,
                       (type %in% c('psi.est', 'theta.est', 'psi.plug.in.est', 'psi.one.step.est',
                       'theta.plug.in.est', 'theta.one.step.est')))[,c("type", "est", "n", "j" , "seed")]
pars.ret <- subset(ests.sim.1.0.0.w.sl,
                       (type %in% 'pars'))[,c("n", "j" , "seed", "psi0", "theta0")]
ests.sim.1.0.0.w.sl.ret <- join(ret, pars.ret, by=c("n", "j", "seed"))
ests.sim.1.0.0.w.sl.optional.ret <- join(optional.ret, pars.ret, by=c("n", "j", "seed"))
psi.summaries <- ddply(subset(ests.sim.1.0.0.w.sl.optional.ret, 
                                (type %in% c('psi.est', 'psi.plug.in.est', 'psi.one.step.est'))),
                                .(n, type), summarize, na = sum(is.na(est)),
                         cnt = length(est),
                         bias = mean(est - psi0, na.rm=TRUE),
                         var = var(est, na.rm=TRUE),
                         mse = mean((est - psi0)^2, na.rm=TRUE))
```


```{r echo=FALSE}
p2 <- ggplot(subset(ests.sim.1.0.0.w.sl.optional.ret, (type %in% 'psi.est'))) + 
  geom_boxplot(aes(as.factor(n), log(1 + sqrt(n) * (est - psi0)), color=type)) +
  # ggtitle(label=paste("convergence of psi", paste(beta, collapse = "_"))) +
  xlab("n") +
  theme(legend.key.size = unit(0.1,"line"))

p3 <- ggplot(subset(ests.sim.1.0.0.w.sl.optional.ret, (type %in% 'psi.plug.in.est'))) + 
  geom_boxplot(aes(as.factor(n), log(1 + sqrt(n) * (est - psi0)), color=type)) +
  # ggtitle(label=paste("convergence of psi", paste(beta, collapse = "_"))) +
  xlab("n") +
  theme(legend.key.size = unit(0.1,"line"))

p4 <- ggplot(subset(ests.sim.1.0.0.w.sl.optional.ret, (type %in% 'psi.one.step.est'))) + 
  geom_boxplot(aes(as.factor(n), log(1 + sqrt(n) * (est - psi0)), color=type)) +
  # ggtitle(label=paste("convergence of psi", paste(beta, collapse = "_"))) +
  xlab("n") +
  theme(legend.key.size = unit(0.1,"line"))

library(gridExtra)
grid.arrange(p2, p3, p4, ncol=2, top = "beta=(0,0)")
```

```{r echo=FALSE}
p2 <- ggplot(psi.summaries) +
  geom_line(aes(n, sqrt(n) * bias, color=type)) +
  theme(legend.key.size = unit(0.1,"line"))

p3 <- ggplot(psi.summaries) +
  geom_line(aes(n, n * mse, color=type)) +
  theme(legend.key.size = unit(0.1,"line"))

p4 <- ggplot(psi.summaries) +
  geom_line(aes(n, n * var, color=type)) +
  # coord_cartesian(ylim=c(0,1)) +
  theme(legend.key.size = unit(0.1,"line"))

library(gridExtra)
grid.arrange(p2, p3, p4, ncol=2, top = "beta=(0,0)")
```

**Estimator of $\theta_0$**
     
```{r echo=FALSE}
theta.summaries <- ddply(subset(ests.sim.1.0.0.w.sl.optional.ret, 
                                (type %in% c('theta.est', 'theta.plug.in.est', 'theta.one.step.est'))),
                                .(n, type), summarize, na = sum(is.na(est)),
                         cnt = length(est),
                         bias = mean(est - theta0, na.rm=TRUE),
                         var = var(est, na.rm=TRUE),
                         mse = mean((est - theta0)^2, na.rm=TRUE))
```

```{r echo=FALSE}
p2 <- ggplot(subset(ests.sim.1.0.0.w.sl.optional.ret, (type %in% 'theta.est'))) + 
  geom_boxplot(aes(as.factor(n), log(1 + sqrt(n) * (est - theta0)), color=type)) +
  # ggtitle(label=paste("convergence of theta", paste(beta, collapse = "_"))) +
  xlab("n") +
  theme(legend.key.size = unit(0.1,"line"))

p3 <- ggplot(subset(ests.sim.1.0.0.w.sl.optional.ret, (type %in% 'theta.plug.in.est'))) + 
  geom_boxplot(aes(as.factor(n), log(1 + sqrt(n) * (est - theta0)), color=type)) +
  # ggtitle(label=paste("convergence of theta", paste(beta, collapse = "_"))) +
  xlab("n") +
  theme(legend.key.size = unit(0.1,"line"))

p4 <- ggplot(subset(ests.sim.1.0.0.w.sl.optional.ret, (type %in% 'theta.one.step.est'))) + 
  geom_boxplot(aes(as.factor(n), log(1 + sqrt(n) * (est - theta0)), color=type)) +
  # ggtitle(label=paste("convergence of theta", paste(beta, collapse = "_"))) +
  xlab("n") +
  theme(legend.key.size = unit(0.1,"line"))

library(gridExtra)
grid.arrange(p2, p3, p4, ncol=2, top = "beta=(0,0)")
```

```{r echo=FALSE}
p2 <- ggplot(theta.summaries) +
  geom_line(aes(n, sqrt(n) * bias, color=type)) +
  theme(legend.key.size = unit(0.1,"line"))

p3 <- ggplot(theta.summaries) +
  geom_line(aes(n, n * mse, color=type)) +
  theme(legend.key.size = unit(0.1,"line"))

p4 <- ggplot(theta.summaries) +
  geom_line(aes(n, n * var, color=type)) +
  # coord_cartesian(ylim=c(0,1)) +
  theme(legend.key.size = unit(0.1,"line"))

library(gridExtra)
grid.arrange(p2, p3, p4, ncol=2, top = "beta=(0,0)")
```


    
## 2 Confidence Intervals

### 2.2 $\beta=(0.25, 0.25)$

The mean of $\psi_0$ is around 0.23.
\

**Wald-type CI for $\psi$**

```{r echo=FALSE}
psi.w.summaries <- ddply(subset(ests.sim.1.25.25.w.sl.ret, (type %in% 'psi.est')), .(n, type), 
                         summarize, na = sum(is.na(est)),
                         coverage = mean(ll <= psi0 & psi0 <= ul, na.rm=TRUE),
                         cnt = length(type))
kable(psi.w.summaries, caption="Wald-type CI coverage for psi0")
```

```{r echo=FALSE}
ests.sim.1.25.25.w.sl.ret$psi.coverage <- (ests.sim.1.25.25.w.sl.ret$ll <= ests.sim.1.25.25.w.sl.ret$psi0) & (ests.sim.1.25.25.w.sl.ret$psi0 <= ests.sim.1.25.25.w.sl.ret$ul)
ggplot(subset(ests.sim.1.25.25.w.sl.ret, (type %in% 'psi.est') & (n %in% c(250, 500, 750, 1000)) & 
                (psi.coverage ==FALSE))) +
  geom_linerange(mapping = aes(x=j, ymin=ll, ymax=ul)) +
  geom_point(mapping=aes(x=j, y=psi0), size=1, col="red") +
  facet_wrap(~n, scales='free') + 
  ggtitle(label="Wald-type CIs failed to cover psi0")
```
      
**Bootstrap CI for $\psi$**
```{r echo=FALSE}
load("../ConfidenceInterval/ests.sim.1.25.25.b.sl.RData")
ret <- subset(ests.sim.1.25.25.b.sl,
              (type %in% c('psi.est', 'theta.est')))[,c("type", "est", "ll", "ul", "n", "j" , "seed")]
pars.ret <- subset(ests.sim.1.25.25.b.sl,
                   (type %in% 'pars'))[,c("n", "j" , "seed", "psi0", "theta0")]
ests.sim.1.25.25.b.sl.ret <- join(ret, pars.ret, by=c("n", "j", "seed"))
```

```{r echo=FALSE}
psi.b.summaries <- ddply(subset(ests.sim.1.25.25.b.sl.ret, (type %in% 'psi.est')), .(n, type), 
                         summarize, na = sum(is.na(est)),
                         coverage = mean(ll <= psi0 & psi0 <= ul, na.rm=TRUE),
                         cnt = length(type))
kable(psi.b.summaries, caption="Bootstrap CI coverage for psi0")
```

```{r echo=FALSE}
ests.sim.1.25.25.b.sl.ret$psi.coverage <- (ests.sim.1.25.25.b.sl.ret$ll <= ests.sim.1.25.25.b.sl.ret$psi0) & (ests.sim.1.25.25.b.sl.ret$psi0 <= ests.sim.1.25.25.b.sl.ret$ul)
ggplot(subset(ests.sim.1.25.25.b.sl.ret, (type %in% 'psi.est') & (n %in% c(250, 500, 750, 1000)) & 
                (psi.coverage ==FALSE))) +
  geom_linerange(mapping = aes(x=j, ymin=ll, ymax=ul)) +
  geom_point(mapping=aes(x=j, y=psi0), size=1, col="red") +
  facet_wrap(~n, scales='free') + 
  ggtitle(label="Bootstrap CIs failed to cover psi0")
```

```{r echo=FALSE}
ggplot() +
  geom_line(data = psi.w.summaries, aes(n, coverage, colour='wald-type')) +
  geom_line(data = psi.b.summaries, aes(n, coverage, colour='bootstrap')) +
  geom_hline(yintercept=.95) +
  ggtitle(label="Confidence interval coverage for psi0")
```

\
The mean of $\theta_0$ is around 0.021.
\
       
**Wald-type CI for $\theta$** 
   
```{r echo=FALSE}
theta.w.summaries <- ddply(subset(ests.sim.1.25.25.w.sl.ret, (type %in% 'theta.est')), .(n, type), 
                         summarize, na = sum(is.na(est)),
                         coverage = mean(ll <= theta0 & theta0 <= ul, na.rm=TRUE),
                         cnt = length(type))
kable(theta.w.summaries, caption="Wald-type CI coverage for theta0")
```

```{r echo=FALSE}
ests.sim.1.25.25.w.sl.ret$theta.coverage <- (ests.sim.1.25.25.w.sl.ret$ll <= ests.sim.1.25.25.w.sl.ret$theta0) & (ests.sim.1.25.25.w.sl.ret$theta0 <= ests.sim.1.25.25.w.sl.ret$ul)
ggplot(subset(ests.sim.1.25.25.w.sl.ret, (type %in% 'theta.est') & (n %in% c(250, 500, 750, 1000)) & 
                (theta.coverage ==FALSE))) +
  geom_linerange(mapping = aes(x=j, ymin=ll, ymax=ul)) +
  geom_point(mapping=aes(x=j, y=theta0), size=1, col="red") +
  facet_wrap(~n, scales='free') + 
  ggtitle(label="Wald-type CIs failed to cover theta0")
```
    
**Bootstrap CI for $\theta$** 
    
```{r echo=FALSE}
theta.b.summaries <- ddply(subset(ests.sim.1.25.25.b.sl.ret, (type %in% 'theta.est')), .(n, type), 
                         summarize, na = sum(is.na(est)),
                         coverage = mean(ll <= theta0 & theta0 <= ul, na.rm=TRUE),
                         cnt = length(type))
kable(theta.b.summaries, caption="Bootstrap CI coverage for theta0")
```

```{r echo=FALSE}
ests.sim.1.25.25.b.sl.ret$theta.coverage <- (ests.sim.1.25.25.b.sl.ret$ll <= ests.sim.1.25.25.b.sl.ret$theta0) & (ests.sim.1.25.25.b.sl.ret$theta0 <= ests.sim.1.25.25.b.sl.ret$ul)
ggplot(subset(ests.sim.1.25.25.b.sl.ret, (type %in% 'theta.est') & (n %in% c(250, 500, 750, 1000)) & 
                (theta.coverage ==FALSE))) +
  geom_linerange(mapping = aes(x=j, ymin=ll, ymax=ul)) +
  geom_point(mapping=aes(x=j, y=theta0), size=1, col="red") +
  facet_wrap(~n, scales='free') + 
  ggtitle(label="Bootstrap CIs failed to cover theta0")
```

```{r echo=FALSE}
ggplot() +
  geom_line(data = theta.w.summaries, aes(n, coverage, colour='wald-type')) +
  geom_line(data = theta.b.summaries, aes(n, coverage, colour='bootstrap')) +
  geom_hline(yintercept=.95) +
  ggtitle(label="Confidence interval coverage for theta0")
``` 
      
## 3 Testing      

### 3.1 $\beta=(0, 0.25)$    
     
$$\psi>0,\quad\theta>0$$

```{r echo=FALSE}
load("../Testing/testing.sim.1.0.25.sl.RData")
```
   
```{r echo=FALSE}
gamma.summaries <- ddply(subset(testing.sim.1.0.25.sl, (type %in% 'Gamma.stat')),
                                   .(n, type), summarize,
                                   na = sum(is.na(stat)),
                                   cnt = length(stat),
                                   # quantile.reject.rate = mean(stat>quantile),
                                   reject.rate = mean(pvalue<0.05))
omega.summaries <- ddply(subset(testing.sim.1.0.25.sl, (type %in% 'Omega.stat')),
                           .(n, type), summarize,
                           na = sum(is.na(stat)),
                           cnt = length(stat),
                           # quantile.reject.rate = mean(stat>quantile),
                           reject.rate = mean(pvalue<0.05))
```



```{r echo=FALSE}
load("../Testing/testing.sim.1.0.25.sl.o.RData")
```

```{r echo=FALSE}
gamma.summaries.o <- ddply(subset(testing.sim.1.0.25.sl.o, (type %in% 'Gamma.omnibus')),
                                   .(n, type), summarize,
                                   na = sum(is.na(stat)),
                                   cnt = length(stat),
                                   # quantile.reject.rate = mean(stat>quantile),
                                   reject.rate = mean(pvalue<0.05))
```

```{r echo=FALSE}
gamma.summaries$omnibus.reject.rate <- gamma.summaries.o$reject.rate
kable(gamma.summaries, caption = "Testing for psi under beta=(0, 0.25)")
```
\
```{r echo=FALSE}
kable(omega.summaries, caption = "Testing for theta under beta=(0, 0.25)")
```

```{r echo=FALSE}
p1 <- ggplot(aes(n, reject.rate, color=type), 
       data=bind_rows(gamma.summaries, gamma.summaries.o)) +
  geom_point() + geom_line() + 
  ggtitle(label=expression(paste(beta, "=(0, 0.25)"))) +
  theme(legend.key.size = unit(0.1,"line"))
```
        
### 3.2 $\beta=(0.25, 0.25)$  
     
$$\psi>0,\quad\theta>0$$
```{r echo=FALSE}
load("../Testing/testing.sim.1.25.25.sl.RData")
```
   
```{r echo=FALSE}
gamma.summaries <- ddply(subset(testing.sim.1.25.25.sl, (type %in% 'Gamma.stat')),
                                   .(n, type), summarize,
                                   na = sum(is.na(stat)),
                                   cnt = length(stat),
                                   # quantile.reject.rate = mean(stat>quantile),
                                   reject.rate = mean(pvalue<0.05))
omega.summaries <- ddply(subset(testing.sim.1.25.25.sl, (type %in% 'Omega.stat')),
                           .(n, type), summarize,
                           na = sum(is.na(stat)),
                           cnt = length(stat),
                           # quantile.reject.rate = mean(stat>quantile),
                           reject.rate = mean(pvalue<0.05))
```


```{r echo=FALSE}
load("../Testing/testing.sim.1.25.25.sl.o.RData")
```

```{r echo=FALSE}
gamma.summaries.o <- ddply(subset(testing.sim.1.25.25.sl.o, (type %in% 'Gamma.omnibus')),
                                   .(n, type), summarize,
                                   na = sum(is.na(stat)),
                                   cnt = length(stat),
                                   # quantile.reject.rate = mean(stat>quantile),
                                   reject.rate = mean(pvalue<0.05))
```

```{r echo=FALSE}
gamma.summaries$omnibus.reject.rate <- gamma.summaries.o$reject.rate
kable(gamma.summaries, caption = "Testing for psi under beta=(0.25, 0.25)")
```
\

```{r echo=FALSE}
kable(omega.summaries, caption = "Testing for theta under beta=(0.25, 0.25)")
```

```{r echo=FALSE}
p2 <- ggplot(aes(n, reject.rate, color=type), 
       data=bind_rows(gamma.summaries, gamma.summaries.o)) +
  geom_point() + geom_line() + 
  ggtitle(label=expression(paste(beta, "=(0.25, 0.25)"))) +
  theme(legend.key.size = unit(0.1,"line"))
```

### 3.3 $\beta=(0.25, 0)$    
          
$$\psi>0,\quad\theta=0$$ 
```{r echo=FALSE}
load("../Testing/testing.sim.1.25.0.sl.RData")
```
   
```{r echo=FALSE}
gamma.summaries <- ddply(subset(testing.sim.1.25.0.sl, (type %in% 'Gamma.stat')),
                                   .(n, type), summarize,
                                   na = sum(is.na(stat)),
                                   cnt = length(stat),
                                   # quantile.reject.rate = mean(stat>quantile),
                                   reject.rate = mean(pvalue<0.05))
omega.summaries <- ddply(subset(testing.sim.1.25.0.sl, (type %in% 'Omega.stat')),
                           .(n, type), summarize,
                           na = sum(is.na(stat)),
                           cnt = length(stat),
                           # quantile.reject.rate = mean(stat>quantile),
                           reject.rate = mean(pvalue<0.05))
```

```{r echo=FALSE}
load("../Testing/testing.sim.1.25.0.sl.o.RData")
```

```{r echo=FALSE}
gamma.summaries.o <- ddply(subset(testing.sim.1.25.0.sl.o, (type %in% 'Gamma.omnibus')),
                                   .(n, type), summarize,
                                   na = sum(is.na(stat)),
                                   cnt = length(stat),
                                   # quantile.reject.rate = mean(stat>quantile),
                                   reject.rate = mean(pvalue<0.05))
```

              
```{r echo=FALSE}
gamma.summaries$omnibus.reject.rate <- gamma.summaries.o$reject.rate
kable(gamma.summaries, caption = "Testing for psi under beta=(0.25, 0)")
```
\
```{r echo=FALSE}
kable(omega.summaries, caption = "Testing for theta under beta=(0.25, 0)")
```

```{r echo=FALSE}
p3 <- ggplot(aes(n, reject.rate, color=type), 
       data=bind_rows(gamma.summaries, gamma.summaries.o)) +
  geom_point() + geom_line() + 
  ggtitle(label=expression(paste(beta, "=(0.25, 0)"))) +
  theme(legend.key.size = unit(0.1,"line"))
```

### 3.4 $\beta=(0, 0)$  
     
$$\psi=0,\quad\theta=0$$
```{r echo=FALSE}
load("../Testing/testing.sim.1.0.0.sl.RData")
```
   
```{r echo=FALSE}
gamma.summaries <- ddply(subset(testing.sim.1.0.0.sl, (type %in% 'Gamma.stat')),
                                   .(n, type), summarize,
                                   na = sum(is.na(stat)),
                                   cnt = length(stat),
                                   # quantile.reject.rate = mean(stat>quantile),
                                   reject.rate = mean(pvalue<0.05))
omega.summaries <- ddply(subset(testing.sim.1.0.0.sl, (type %in% 'Omega.stat')),
                           .(n, type), summarize,
                           na = sum(is.na(stat)),
                           cnt = length(stat),
                           # quantile.reject.rate = mean(stat>quantile),
                           reject.rate = mean(pvalue<0.05))
```


```{r echo=FALSE}
load("../Testing/testing.sim.1.0.0.sl.o.RData")
```

```{r echo=FALSE}
gamma.summaries.o <- ddply(subset(testing.sim.1.0.0.sl.o, (type %in% 'Gamma.omnibus')),
                                   .(n, type), summarize,
                                   na = sum(is.na(stat)),
                                   cnt = length(stat),
                                   # quantile.reject.rate = mean(stat>quantile),
                                   reject.rate = mean(pvalue<0.05))
```

```{r echo=FALSE}
gamma.summaries$omnibus.reject.rate <- gamma.summaries.o$reject.rate
kable(gamma.summaries, caption = "Testing for psi under beta=(0, 0)")
```
\

```{r echo=FALSE}
kable(omega.summaries, caption = "Testing for theta under beta=(0, 0)")
```

```{r echo=FALSE}
p4 <- ggplot(aes(n, reject.rate, color=type), 
       data=bind_rows(gamma.summaries, gamma.summaries.o)) +
  geom_point() + geom_line() + 
  ggtitle(label=expression(paste(beta, "=(0, 0)"))) + 
  theme(legend.key.size = unit(0.1,"line"))

grid.arrange(p1, p2, p3, p4, ncol=2)
```